\LARGE \bf Planning with Attitude

### 2020-10-14 paper/main.tex

        The solver was initialized with level flight trim
        conditions. The convergence of the different versions of ALTRO is compared in
        Fig. \ref{fig:c_max_convergence}. As expected, the modified version achieves
        better convergence and faster solve times compared to the na\"ive version since
        the expansions being provided to the algorithm more accurately capture the
        relationship between the attitude state and the goal and constraints. For this 
        relatively simple problem, we gained a modest 7\% improvement in runtime, despite
        the additional matrix multiplications when calculating the cost and constraint
        expansions.

        \begin{figure}[ht]
            \centering
            \includegraphics[width=\columnwidth]{figures/barrellroll.png}
            \caption{Barrel roll trajectory computed by ALTRO using a terminal cost to encourage an upside-down attitude.}
            \label{fig:barrellroll}
        \end{figure}

        \begin{figure}[ht]
            \centering
            \includegraphics[height=4cm,width=\columnwidth]{figures/c_max_convergence.tikz}
            \caption{Constraint satisfaction as a function of iteration when solving the barrel roll problem using ALTRO both with and without the modifications for optimizing unit quaternions.}
            \label{fig:c_max_convergence}
        \end{figure}

    \subsection{Quadrotor Flip}
        A 360 degree flip trajectory for a quadrotor was optimized with dynamics adapted
        from \cite{mellinger2012trajectory}. To encourage the flip, we specified a 
        ``waypoint'' cost function of the following form:
        \begin{multline}
                  \sum_{k \in \mathcal{N}} \ell(x_k, \hat{x}, \hat{Q}) 
                + \sum_{k \in \mathcal{W}} \ell(x_k, \bar{x}_k, Q_w) 
                + \half \sum_{k=1} u_k^T R u_k
        \end{multline}
        with $\mathcal{W} = \{45,51,55,75,101\}$, $\mathcal{N} = \{1:101\} \setminus
        \mathcal{W}$. The four intermediary ``waypoints'' were used to encourage the
        quadrotor to reach angles of \ang{90}, \ang{180}, \ang{270}, and \ang{360} around
        an approximately circular arc. The last waypoint was used to encourage the
        quadrotor to move towards the final goal. The quadrotor was constrained to stay
        above the floor and move to a goal state two meters away in the $+y$ direction. The
        solver was provided a dynamically infeasible initial trajectory that linearly
        interpolates between the initial and final states, rotating the quadrotor around
        the x-axis a full \ang{360}.

>>>>

        The solver was initialized with level flight trim
        conditions. The convergence of the different versions of ALTRO is compared in
        Fig. \ref{fig:c_max_convergence}. As expected, the modified version achieves
        better convergence and faster solve times compared to the na\"ive version since
        the expansions being provided to the algorithm more accurately capture the
        relationship between the attitude state and the goal and constraints. For this 
        relatively simple problem, we gained a modest 11\% improvement in runtime, despite
        the additional matrix multiplications when calculating the cost and constraint
        expansions.

        \begin{figure}[t]
            \centering
            \includegraphics[width=\columnwidth]{figures/barrellroll.png}
            \caption{Barrel roll trajectory computed by ALTRO using a terminal cost to encourage an upside-down attitude.}
            \label{fig:barrellroll}
        \end{figure}

        \begin{figure}[t]
            \centering
            \includegraphics[height=4cm,width=\columnwidth]{figures/c_max_convergence.tikz}
            \caption{Constraint satisfaction as a function of iteration when solving the barrel roll problem using ALTRO both with and without the modifications for optimizing unit quaternions.}
            \label{fig:c_max_convergence}
        \end{figure}

    \subsection{Quadrotor Flip}
        A 360 degree flip trajectory for a quadrotor was optimized with dynamics adapted
        from \cite{mellinger2012trajectory}. To encourage the flip, we specified a 
        ``waypoint'' cost function of the following form:
        \begin{multline}
                  \sum_{k \in \mathcal{N}} \ell(x_k, u_k, \hat{x}, \hat{Q}, R) 
                + \sum_{k \in \mathcal{W}} \ell(x_k, u_k, \bar{x}_k, Q_w, R) 
        \end{multline}
        where $\hat{x}$, $\hat{Q}$ are the nominal state and state weight matrix, $Q_w$ is 
        the weight matrix for the waypoints, and
        $\mathcal{W} = \{45,51,55,75,101\}$, $\mathcal{N} = \{1:101\} \setminus
        \mathcal{W}$.
        Four intermediary ``waypoints'' were used to encourage the
        quadrotor to reach angles of \ang{90}, \ang{180}, \ang{270}, and \ang{360} around
        an approximately circular arc. The last waypoint was used to encourage the
        quadrotor to move towards the final goal. The quadrotor was constrained to stay
        above the floor and move to a goal state two meters away in the $+y$ direction. The
        solver was provided a dynamically infeasible initial trajectory that linearly
        interpolates between the initial and final states, rotating the quadrotor around
        the x-axis a full \ang{360}.
